Supplementary Information -- Morphological convergence as on-line lexical analogy

### 2020-02-20 supplementary_information/si.Rnw
nice sig

# libraries
library(tidyverse) # for data wrangling, figures
library(purrr) # for functional programming
library(stringr) # for string manipulation
library(readr) # for reading
library(scales) # for rescaling
library(xtable) # for latex tables
library(lme4) # for GLMM-s

@@

# In the next par, I won't pipe the values into variables in the text, but you can look them up here:
splive_mgl_rules = mgl_baseline_rules_raw %>% 
  dplyr::filter(
    form1 == 'spl2v'
  )
# regular
splive_mgl_rules[3,]$Pfeat
splive_mgl_rules[3,]$hits
splive_mgl_rules[3,]$scope
splive_mgl_rules[3,]$reliability
splive_mgl_rules[3,]$confidence

# irregular
splive_mgl_rules[1,]$Pfeat
splive_mgl_rules[1,]$hits
splive_mgl_rules[1,]$scope
splive_mgl_rules[1,]$`related forms`
splive_mgl_rules[1,]$exceptions
splive_mgl_rules[1,]$reliability
splive_mgl_rules[1,]$confidence

@@

The two past forms of {\em splive} in the experiment are regular {\em splived} and irregular {\em splove}. The {\em relevant regular rule} that generates the regular past tense is `$\emptyset{} \rightarrow{}$ \textipa{[d]} / \{\textipa{D}, \textipa{S}, \textipa{T}, \textipa{Z}, f, s, v, z\} \underline{\hspace{0.5cm}}'. The {\em structural description} indicates that this is a suffixation rule that can apply to forms that {\em end in an anterior fricative} (a natural class in our feature system).  The {\em raw confidence} of this rule is 0.98. This is because this rule applies to most forms in its scope (698/712). The {\em adjusted confidence} is very similar: 0.968. This is because this rule applies to a large number of forms overall. The {\em relevant irregular rule} that generates the irregular form is `\textipa{[aI]} $\rightarrow{}$ \textipa{[oU]} / \{\textipa{D}, \textipa{Z}, \textipa{dZ}, d, l, n, r, z\} \underline{\hspace{0.5cm}}v'. It applies to \textipa{[aI]} in the nucleus {\em preceded by voiced anterior consonant and followed by \textipa{[v]}}. In \textsc{Celex},the rule applies to three forms ({\em drive, strive, dive}) and fails to apply to five ({\em arrive, thrive, contrive, rive, connive}). Its {\em raw confidence} is 0.375. Its {\em adjusted confidence} is slightly lower (0.366). This is because it applies to a smaller number of forms overall. The {\em relative (adjusted) confidence} of the predicted regularity of {\em splive} is $0.98/(0.98+0.37)=0.73$. The respective rescaled value is 0.363.

@@

<<main_model1, echo=F,eval=T>>=

##########################################
# VIF for GLMM-s, from Florian Jaeger

vif.mer <- function (fit) {
  ## adapted from rms::vif
  v <- vcov(fit)
  nam <- names(fixef(fit))
  ## exclude intercepts
  ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
  if (ns > 0) {
    v <- v[-(1:ns), -(1:ns), drop = FALSE]
    nam <- nam[-(1:ns)] }
  d <- diag(v)^0.5
  v <- diag(solve(v/(d %o% d)))
  names(v) <- nam 
  v 
  }
@

@@

<<main_model3, echo=F,eval=T, results=tex>>=
load('models/si_fit1.rda')
print(xtable::xtable(summary(lme.fit1)$coef, digits = 3, label = 'regressiontable1', caption = 'Experimental Data, Post-test Regression Model Summary. Model formula: post-test regular response ~ verb baseline mean x lexical typicality + participant pretest mean + regularization shift + (1 + verb.baseline.mean | participant) + (1 | verb)'))
@

@@

<<celex_resid1, echo=F,eval=T, results=tex>>=
load('models/si_celex_m3.rda')
print(xtable::xtable(summary(celex_m3)$coef, digits = 3, label = 'resid1', caption = 'Model 3: MGL scores and GCM residuals, baseline data'))
@

<<celex_resid2, echo=F,eval=T, results=tex>>=
load('models/si_celex_m4.rda')
print(xtable::xtable(summary(celex_m4)$coef, digits = 3, label = 'resid2', caption = 'Model 4: GCM scores and MGL residuals, baseline data'))
@

@@

<<indiv_diff1, echo=F, eval=T, results=tex>>=

load('models/si_indiv_m5.rda')
print(xtable::xtable(summary(indiv_m5)$coef, digits = 3, label = 'indiv1', caption = 'Model 5: Celex-GCM and individual score difference, post-test data'))

@@

<<indiv_diff2, echo=F,eval=T, results=tex>>=
load('models/si_indiv_m6.rda')
print(xtable::xtable(summary(indiv_m6)$coef, digits = 3, label = 'indiv2', caption = 'Model 6: Celex-MGL and individual score difference, post-test data'))
@

@@

<<comparison_model3, echo=F,eval=T, results=tex>>=
print(xtable::xtable(summary(comp_fit1)$coef, digits = 3, label = 'comp3', caption = 'Celex-MGL and Individual-GCM predict variation in the post-test'))
@

>>>>

# libraries
library(tidyverse) # for data wrangling, figures
library(purrr) # for functional programming
library(stringr) # for string manipulation
library(readr) # for reading
library(scales) # for rescaling
library(xtable) # for latex tables
library(lme4) # for GLMM-s
library(broom) # for tidy summaries

# functions

niceCoefTable = function(fit){
  my_table = fit %>% 
    tidy %>% 
    filter(
      group == 'fixed'
    ) %>% 
    mutate(
      sig = case_when(
        p.value >= 0.05 ~ 'n.s.',
        p.value < 0.05 & p.value >= 0.01 ~ '*',
        p.value < 0.01 & p.value >= 0.001 ~ '**',
        p.value < 0.001 ~ '***'
      )
    ) %>% 
    select(
      - p.value,
      - group
    )
return(my_table)  
}

# VIF for GLMM-s, from Florian Jaeger

vif.mer <- function (fit) {
  ## adapted from rms::vif
  v <- vcov(fit)
  nam <- names(fixef(fit))
  ## exclude intercepts
  ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
  if (ns > 0) {
    v <- v[-(1:ns), -(1:ns), drop = FALSE]
    nam <- nam[-(1:ns)] }
  d <- diag(v)^0.5
  v <- diag(solve(v/(d %o% d)))
  names(v) <- nam 
  v 
  }

@@

# In the next par, I won't pipe the values into variables in the text, but you can look them up here:
splive_mgl_rules = mgl_baseline_rules_raw %>% 
  dplyr::filter(
    form1 == 'spl2v'
  )
# regular
splive_mgl_rules[splive_mgl_rules$B == 'd',]$Pfeat
splive_mgl_rules[splive_mgl_rules$B == 'd',]$hits
splive_mgl_rules[splive_mgl_rules$B == 'd',]$scope
splive_mgl_rules[splive_mgl_rules$B == 'd',]$reliability
splive_mgl_rules[splive_mgl_rules$B == 'd',]$confidence

# irregular
splive_mgl_rules[splive_mgl_rules$B == 'o',]$Pfeat # this kept the original transcription that we change to DISC 5 in form2
splive_mgl_rules[splive_mgl_rules$B == 'o',]$hits
splive_mgl_rules[splive_mgl_rules$B == 'o',]$scope
splive_mgl_rules[splive_mgl_rules$B == 'o',]$`related forms`
splive_mgl_rules[splive_mgl_rules$B == 'o',]$exceptions
splive_mgl_rules[splive_mgl_rules$B == 'o',]$reliability
splive_mgl_rules[splive_mgl_rules$B == 'o',]$confidence

@@

The two past forms of {\em splive} in the experiment are regular {\em splived} and irregular {\em splove}. The {\em relevant regular rule} that generates the regular past tense is `$\emptyset{} \rightarrow{}$ \textipa{[d]} / \{\textipa{D}, \textipa{S}, \textipa{T}, \textipa{Z}, f, s, v, z\} \underline{\hspace{0.5cm}}'. The {\em structural description} indicates that this is a suffixation rule that can apply to forms that {\em end in an anterior fricative} (a natural class in our feature system).  The {\em raw confidence} of this rule is 0.98. This is because this rule applies to most forms in its scope (698/712). The {\em adjusted confidence} is very similar: 0.968. This is because this rule applies to a large number of forms overall. The {\em relevant irregular rule} that generates the irregular form is `\textipa{[aI]} $\rightarrow{}$ \textipa{[oU]} / \{\textipa{D}, \textipa{Z}, \textipa{dZ}, d, l, n, r, z\} \underline{\hspace{0.5cm}}v'. It applies to \textipa{[aI]} in the nucleus {\em preceded by voiced anterior consonant and followed by \textipa{[v]}}. In \textsc{Celex},the rule applies to three forms ({\em drive, strive, dive}) and fails to apply to five ({\em arrive, thrive, contrive, rive, connive}). Its {\em raw confidence} is 0.375. Its {\em adjusted confidence} is slightly lower (0.366). This is because it applies to a smaller number of forms overall. The {\em relative (adjusted) confidence} of the predicted regularity of {\em splive} is $0.98/(0.98+0.37)=0.73$. (The respective rescaled value is 0.363 -- which, in itself, is not very informative.)

@@

@@

<<main_model3, echo=F,eval=T, results=tex>>=
load('models/si_fit1.rda')
lme.fit1.sum = niceCoefTable(lme.fit1)

print(xtable::xtable(lme.fit1.sum, digits = 2, label = 'regressiontable1', caption = 'Experimental Data, Post-test Regression Model Summary. Model formula: post-test regular response ~ verb baseline mean x lexical typicality + participant pretest mean + regularization shift + (1 + verb.baseline.mean | participant) + (1 | verb)'))
@

@@

<<celex_resid1, echo=F,eval=T, results=tex>>=
load('models/si_celex_m3.rda')
celex_m3_summary = niceCoefTable(celex_m3)
print(xtable::xtable(celex_m3_summary, digits = 2, label = 'resid1', caption = 'Model 3: MGL scores and GCM residuals, baseline data'))
@

<<celex_resid2, echo=F,eval=T, results=tex>>=
load('models/si_celex_m4.rda')
celex_m4_summary = niceCoefTable(celex_m4)
print(xtable::xtable(celex_m4_summary, digits = 2, label = 'resid2', caption = 'Model 4: GCM scores and MGL residuals, baseline data'))
@

@@

<<indiv_diff1, echo=F, eval=T, results=tex>>=
load('models/si_indiv_m5.rda')
indiv_m5_sum = niceCoefTable(indiv_m5)
print(xtable::xtable(indiv_m5_sum, digits = 2, label = 'indiv1', caption = 'Model 5: Celex-GCM and individual score difference, post-test data'))

@@

<<indiv_diff2, echo=F,eval=T, results=tex>>=
load('models/si_indiv_m6.rda')
indiv_m6_sum = niceCoefTable(indiv_m6)
print(xtable::xtable(indiv_m6_sum, digits = 3, label = 'indiv2', caption = 'Model 6: Celex-MGL and individual score difference, post-test data'))
@

@@

<<comparison_model3, echo=F,eval=T, results=tex>>=
comp_fit1_sum = niceCoefTable(comp_fit1)
print(xtable::xtable(comp_fit1_sum, digits = 2, label = 'comp3', caption = 'Celex-MGL and Individual-GCM predict variation in the post-test'))
@

### 2020-02-20 supplementary_information/si.tex
nice sig

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:14 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllll}
  \hline
 & verb class & irregular set & regular set & miscellaneous regular verbs \\ 
  \hline
1 & BURNT & 6 & 42 & 1218 \\ 
  2 & DROVE & 14 & 83 & 1218 \\ 
  3 & KEPT & 12 & 31 & 1218 \\ 
  4 & SANG & 8 & 13 & 1218 \\ 
  5 & sum & 40 & 169 & 1218 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, GCM training data} 
\label{gcmsetsize}
\end{table}
\subsection{Estimation}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:14 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllrr}
  \hline
 & category & rule.type & related forms & exceptions \\ 
  \hline
1 & burnt & irregular &  24 &  41 \\ 
  2 & drove & irregular &  21 & 114 \\ 
  3 & kept & irregular &  10 &   9 \\ 
  4 & sang & irregular &  11 &  77 \\ 
  5 & burnt & regular &  38 &  21 \\ 
  6 & drove & regular &  29 &  27 \\ 
  7 & kept & regular &  67 &  41 \\ 
  8 & sang & regular &  47 &  38 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, MGL training data} 
\label{mglsetsize}
\end{table}
\subsection{Estimation}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:14 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllrr}
  \hline
 & category & rule.type & related forms & exceptions \\ 
  \hline
1 & burnt & irregular &  24 &  41 \\ 
  2 & drove & irregular &  21 & 114 \\ 
  3 & kept & irregular &  10 &   9 \\ 
  4 & sang & irregular &  11 &  77 \\ 
  5 & burnt & regular &  38 &  21 \\ 
  6 & drove & regular &  29 &  27 \\ 
  7 & kept & regular &  67 &  41 \\ 
  8 & sang & regular &  47 &  38 \\ 
   \hline
\end{tabular}
\caption{The number of unique rules posited by the MGL in each verb class} 
\label{mglruleses}
\end{table}
Table \ref{mglruleseskept} shows the list of (irregular and regular) rules for one of the classes, the KEPT class. We choose this class as it provides a good illustration of the estimation process. An MGL rule describes an $A \rightarrow{} B$ {\em alternation} in an $XAY$ {\em environment}. Since the KEPT rules are all suffixing, the following environment ($Y$) is empty. For the preceding environment ($X$), we give a list of segments that are matched by the structural description if it applies to four segments or fewer. Otherwise, we give a phonological description. So, for instance, the first rule turns \textipa{[il]} to \textipa{[Elt]} following any obstruent. Note that in some cases, the MGL generates multiple rules for the same alternation (such as \textipa{ip} $\rightarrow{}$ \textipa{Ept}). As discussed in Section \ref{mgloutput}, in such instances, we choose the candidate rule with the highest adjusted confidence in order to calculate the MGL regularity score. (Fricatives and nasal consonants constitute a natural class in the segmental feature system used by \citealt{albright2003rules}.)

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:14 2020
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -0.108 & 0.161 & -0.672 & 0.501 \\ 
  verb\_baseline\_average & 8.259 & 0.686 & 12.040 & 0.000 \\ 
  bot\_lexical\_typicalityrandom & 0.043 & 0.169 & 0.253 & 0.800 \\ 
  bot\_lexical\_typicalityreversed & 0.035 & 0.173 & 0.204 & 0.839 \\ 
  participant\_prereg\_average & 7.125 & 0.563 & 12.667 & 0.000 \\ 
  bot\_regularisation\_rate-40\% & -0.456 & 0.185 & -2.468 & 0.014 \\ 
  bot\_regularisation\_rate+40\% & 0.549 & 0.166 & 3.307 & 0.001 \\ 
  verb\_baseline\_average:bot\_lexical\_typicalityrandom & -2.402 & 0.927 & -2.591 & 0.010 \\ 
  verb\_baseline\_average:bot\_lexical\_typicalityreversed & -2.127 & 0.955 & -2.226 & 0.026 \\ 
   \hline
\end{tabular}
\caption{Experimental Data, Post-test Regression Model Summary. Model formula: post-test regular response ~ verb baseline mean x lexical typicality + participant pretest mean + regularization shift + (1 + verb.baseline.mean | participant) + (1 | verb)} 
\label{regressiontable1}
\end{table}
Our regression model selection in this article proceeded as follows. Except where stated otherwise, we fit logistic mixed-effects regression models, using R's lme4 package \citep{bateslme4}. Non-significant predictors are removed from our models, as determined by a series of comparisons of nested models, using likelihood ratio tests in R's anova function. However, our model tables (e.g., Tables 5 and 6 in the main text) include the significance levels generated by lme4 summaries.

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:16 2020
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -0.525 & 0.124 & -4.219 & 0.000 \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.347 & 0.093 & 14.482 & 0.000 \\ 
  rescaled\_CELEX\_gcm\_feature\_distance\_residual & 1.423 & 0.128 & 11.100 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model 3: MGL scores and GCM residuals, baseline data} 
\label{resid1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:16 2020
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -1.225 & 0.160 & -7.682 & 0.000 \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 2.391 & 0.149 & 16.063 & 0.000 \\ 
  rescaled\_CELEX\_mgl\_feature\_distance\_residual & 1.008 & 0.090 & 11.154 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model 4: GCM scores and MGL residuals, baseline data} 
\label{resid2}
\end{table}
Model 1 predicts the GCM scores from the MGL scores (M1: GCM regular score  $\sim$ MGL regular score). Model 2 predicts the MGL scores from the GCM scores (M2: MGL regular score  $\sim$ GCM regular score). In two additional models, we then use the residuals from each model (M1, M2) as an estimate of the variation present in one score that cannot be attributed to the other.  First, we use the residuals of Model 1 in another, mixed-effects logistic regression model along with the MGL scores to predict regular responses in the baseline task (M3: regular response  $\sim$ MGL score + GCM residual + (1 + MGL score + GCM residual$|$participant) + (1 $|$ verb)). We then residualize for the MGL. We use the residuals of Model 2 along with the GCM scores in a similar logistic regression model (M4: regular response  $\sim$ GCM score + MGL residual + (1 + GCM score + MGL residual $|$participant)).

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:16 2020
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -2.951 & 0.295 & -10.007 & 0.000 \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 4.369 & 0.425 & 10.284 & 0.000 \\ 
  gcm\_score\_diff & 2.612 & 0.470 & 5.563 & 0.000 \\ 
  participant\_prereg\_average & 5.289 & 0.602 & 8.788 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model 5: Celex-GCM and individual score difference, post-test data} 
\label{indiv1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:17 2020
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -1.318 & 0.152 & -8.663 & 0.000 \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.944 & 0.176 & 11.045 & 0.000 \\ 
  mgl\_score\_diff & 0.304 & 0.139 & 2.181 & 0.029 \\ 
  participant\_prereg\_average & 7.203 & 0.591 & 12.190 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model 6: Celex-MGL and individual score difference, post-test data} 
\label{indiv2}
\end{table}
We do this for both the GCM  (Model 5: regular response  $\sim$ \textsc{Celex} GCM score + extra GCM information + participant pre-test mean + (1 + \textsc{Celex} GCM + extra GCM information$|$participant) + (1$|$verb) and the MGL (Model 6: regular response  $\sim$ \textsc{Celex} MGL score + extra MGL information + participant pre-test mean + (1 + \textsc{Celex} MGL + extra MGL information$|$participant)+ (1$|$verb)).

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Feb 19 11:30:17 2020
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -2.942 & 0.270 & -10.896 & 0.000 \\ 
  r\_baseline\_mgl\_features & 1.600 & 0.171 & 9.361 & 0.000 \\ 
  r\_individual\_gcm\_features & 2.786 & 0.378 & 7.369 & 0.000 \\ 
  participant\_prereg\_average & 5.437 & 0.585 & 9.298 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Celex-MGL and Individual-GCM predict variation in the post-test} 
\label{comp3}
\end{table}
Goodness-of-fit tests show that model fit is significantly worse if we exclude {\sc Celex}-MGL ($\chi^2 = $ 201.86) or individual-GCM ($\chi^2 = $ 81.82) as predictors. It is not significantly better if we include individual-MGL ($\chi^2 = $ 0.09) or {\sc Celex}-GCM ($\chi^2 = $ 2.03).

>>>>

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:10 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllll}
  \hline
 & verb class & irregular set & regular set & miscellaneous regular verbs \\ 
  \hline
1 & BURNT & 6 & 42 & 1218 \\ 
  2 & DROVE & 14 & 83 & 1218 \\ 
  3 & KEPT & 12 & 31 & 1218 \\ 
  4 & SANG & 8 & 13 & 1218 \\ 
  5 & sum & 40 & 169 & 1218 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, GCM training data} 
\label{gcmsetsize}
\end{table}
\subsection{Estimation}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:10 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllrr}
  \hline
 & category & rule.type & related forms & exceptions \\ 
  \hline
1 & burnt & irregular &  24 &  41 \\ 
  2 & drove & irregular &  21 & 114 \\ 
  3 & kept & irregular &  10 &   9 \\ 
  4 & sang & irregular &  11 &  77 \\ 
  5 & burnt & regular &  38 &  21 \\ 
  6 & drove & regular &  29 &  27 \\ 
  7 & kept & regular &  67 &  41 \\ 
  8 & sang & regular &  47 &  38 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, MGL training data} 
\label{mglsetsize}
\end{table}
\subsection{Estimation}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:10 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllrr}
  \hline
 & category & rule.type & related forms & exceptions \\ 
  \hline
1 & burnt & irregular &  24 &  41 \\ 
  2 & drove & irregular &  21 & 114 \\ 
  3 & kept & irregular &  10 &   9 \\ 
  4 & sang & irregular &  11 &  77 \\ 
  5 & burnt & regular &  38 &  21 \\ 
  6 & drove & regular &  29 &  27 \\ 
  7 & kept & regular &  67 &  41 \\ 
  8 & sang & regular &  47 &  38 \\ 
   \hline
\end{tabular}
\caption{The number of unique rules posited by the MGL in each verb class} 
\label{mglruleses}
\end{table}
Table \ref{mglruleseskept} shows the list of (irregular and regular) rules for one of the classes, the KEPT class. We choose this class as it provides a good illustration of the estimation process. An MGL rule describes an $A \rightarrow{} B$ {\em alternation} in an $XAY$ {\em environment}. Since the KEPT rules are all suffixing, the following environment ($Y$) is empty. For the preceding environment ($X$), we give a list of segments that are matched by the structural description if it applies to four segments or fewer. Otherwise, we give a phonological description. So, for instance, the first rule turns \textipa{[il]} to \textipa{[Elt]} following any obstruent. Note that in some cases, the MGL generates multiple rules for the same alternation (such as \textipa{ip} $\rightarrow{}$ \textipa{Ept}). As discussed in Section \ref{mgloutput}, in such instances, we choose the candidate rule with the highest adjusted confidence in order to calculate the MGL regularity score. (Fricatives and nasal consonants constitute a natural class in the segmental feature system used by \citealt{albright2003rules}.)

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:10 2020
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrl}
  \hline
 & term & estimate & std.error & statistic & sig \\ 
  \hline
1 & (Intercept) & -0.11 & 0.16 & -0.67 & n.s. \\ 
  2 & verb\_baseline\_average & 8.26 & 0.69 & 12.04 & *** \\ 
  3 & bot\_lexical\_typicalityrandom & 0.04 & 0.17 & 0.25 & n.s. \\ 
  4 & bot\_lexical\_typicalityreversed & 0.04 & 0.17 & 0.20 & n.s. \\ 
  5 & participant\_prereg\_average & 7.13 & 0.56 & 12.67 & *** \\ 
  6 & bot\_regularisation\_rate-40\% & -0.46 & 0.18 & -2.47 & * \\ 
  7 & bot\_regularisation\_rate+40\% & 0.55 & 0.17 & 3.31 & *** \\ 
  8 & verb\_baseline\_average:bot\_lexical\_typicalityrandom & -2.40 & 0.93 & -2.59 & ** \\ 
  9 & verb\_baseline\_average:bot\_lexical\_typicalityreversed & -2.13 & 0.96 & -2.23 & * \\ 
   \hline
\end{tabular}
\caption{Experimental Data, Post-test Regression Model Summary. Model formula: post-test regular response ~ verb baseline mean x lexical typicality + participant pretest mean + regularization shift + (1 + verb.baseline.mean | participant) + (1 | verb)} 
\label{regressiontable1}
\end{table}
Our regression model selection in this article proceeded as follows. Except where stated otherwise, we fit logistic mixed-effects regression models, using R's lme4 package \citep{bateslme4}. Non-significant predictors are removed from our models, as determined by a series of comparisons of nested models, using likelihood ratio tests in R's anova function. However, our model tables (e.g., Tables 5 and 6 in the main text) include the significance levels generated by lme4 summaries.

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:11 2020
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrl}
  \hline
 & term & estimate & std.error & statistic & sig \\ 
  \hline
1 & (Intercept) & -0.53 & 0.12 & -4.22 & *** \\ 
  2 & rescaled\_CELEX\_mgl\_feature\_distance & 1.35 & 0.09 & 14.48 & *** \\ 
  3 & rescaled\_CELEX\_gcm\_feature\_distance\_residual & 1.42 & 0.13 & 11.10 & *** \\ 
   \hline
\end{tabular}
\caption{Model 3: MGL scores and GCM residuals, baseline data} 
\label{resid1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:12 2020
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrl}
  \hline
 & term & estimate & std.error & statistic & sig \\ 
  \hline
1 & (Intercept) & -1.23 & 0.16 & -7.68 & *** \\ 
  2 & rescaled\_CELEX\_gcm\_feature\_distance & 2.39 & 0.15 & 16.06 & *** \\ 
  3 & rescaled\_CELEX\_mgl\_feature\_distance\_residual & 1.01 & 0.09 & 11.15 & *** \\ 
   \hline
\end{tabular}
\caption{Model 4: GCM scores and MGL residuals, baseline data} 
\label{resid2}
\end{table}
Model 1 predicts the GCM scores from the MGL scores (M1: GCM regular score  $\sim$ MGL regular score). Model 2 predicts the MGL scores from the GCM scores (M2: MGL regular score  $\sim$ GCM regular score). In two additional models, we then use the residuals from each model (M1, M2) as an estimate of the variation present in one score that cannot be attributed to the other.  First, we use the residuals of Model 1 in another, mixed-effects logistic regression model along with the MGL scores to predict regular responses in the baseline task (M3: regular response  $\sim$ MGL score + GCM residual + (1 + MGL score + GCM residual$|$participant) + (1 $|$ verb)). We then residualize for the MGL. We use the residuals of Model 2 along with the GCM scores in a similar logistic regression model (M4: regular response  $\sim$ GCM score + MGL residual + (1 + GCM score + MGL residual $|$participant)).

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:12 2020
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrl}
  \hline
 & term & estimate & std.error & statistic & sig \\ 
  \hline
1 & (Intercept) & -2.95 & 0.29 & -10.01 & *** \\ 
  2 & rescaled\_CELEX\_gcm\_feature\_distance & 4.37 & 0.42 & 10.28 & *** \\ 
  3 & gcm\_score\_diff & 2.61 & 0.47 & 5.56 & *** \\ 
  4 & participant\_prereg\_average & 5.29 & 0.60 & 8.79 & *** \\ 
   \hline
\end{tabular}
\caption{Model 5: Celex-GCM and individual score difference, post-test data} 
\label{indiv1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:12 2020
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrl}
  \hline
 & term & estimate & std.error & statistic & sig \\ 
  \hline
1 & (Intercept) & -1.318 & 0.152 & -8.663 & *** \\ 
  2 & rescaled\_CELEX\_mgl\_feature\_distance & 1.944 & 0.176 & 11.045 & *** \\ 
  3 & mgl\_score\_diff & 0.304 & 0.139 & 2.181 & * \\ 
  4 & participant\_prereg\_average & 7.203 & 0.591 & 12.190 & *** \\ 
   \hline
\end{tabular}
\caption{Model 6: Celex-MGL and individual score difference, post-test data} 
\label{indiv2}
\end{table}
We do this for both the GCM  (Model 5: regular response  $\sim$ \textsc{Celex} GCM score + extra GCM information + participant pre-test mean + (1 + \textsc{Celex} GCM + extra GCM information$|$participant) + (1$|$verb) and the MGL (Model 6: regular response  $\sim$ \textsc{Celex} MGL score + extra MGL information + participant pre-test mean + (1 + \textsc{Celex} MGL + extra MGL information$|$participant)+ (1$|$verb)).

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu Feb 20 11:18:12 2020
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrl}
  \hline
 & term & estimate & std.error & statistic & sig \\ 
  \hline
1 & (Intercept) & -2.94 & 0.27 & -10.90 & *** \\ 
  2 & r\_baseline\_mgl\_features & 1.60 & 0.17 & 9.36 & *** \\ 
  3 & r\_individual\_gcm\_features & 2.79 & 0.38 & 7.37 & *** \\ 
  4 & participant\_prereg\_average & 5.44 & 0.58 & 9.30 & *** \\ 
   \hline
\end{tabular}
\caption{Celex-MGL and Individual-GCM predict variation in the post-test} 
\label{comp3}
\end{table}
Goodness-of-fit tests show that model fit is significantly worse if we exclude {\sc Celex}-MGL ($\chi^2 = $ 201.86) or individual-GCM ($\chi^2 = $ 81.82) as predictors. It is not significantly better if we include individual-MGL ($\chi^2 = $ 0.09) or {\sc Celex}-GCM ($\chi^2 = $ 2.03).
